A primer to numerical simulations: The perihelion motion of Mercury

### 2017-12-07 tex/MercuryNumerical.tex
English ball in the box example

Instead of providing the template to the students, they could build the program from scratch.
Of course, this requires some basic knowledge in \texttt{VPython}, as they could acquire for example by working through a ball in the box example\cite{}\todo{@IH: cite ball in the box} or the like.
Also, they could independently research the problem relevant parameters.
\item \textbf{Why can we work in one plane?}

>>>>

Instead of providing the template to the students, they could build the program from scratch.
Of course, this requires some basic knowledge in \texttt{VPython}, as they could acquire for example by working through a ball in the box example (see~\url{http://www.vpython.org/contents/docs/VPython_Intro.pdf}) or the like.
Also, they could independently research the problem relevant parameters.
\item \textbf{Why can we work in one plane?}
